\pdftitle

### 2017-05-16 maxNt.tex
working on a short introduction regarding the neuroscience background

 used in neuroscience to study the patterns of neuronal
 firing in relation to stimuli or behavioral tasks. These studies strive for understanding the 
mechanism behind neuronal coding. 
 by answering
 questions such as, which level of interaction (pairwise or higher-order) between neurons
 is suffiecient to explain the observed experimental data [\cite]? Or how collective behavior
 of neurons can be related to stimuli or behavioral tasks [\cite]? These questions 
**********
\mynote{Version 1}
The present note has three nested purposes.

>>>>

 These studies strive for answering 
 questions such as, which level of interaction (pairwise or higher-order) between neurons
 is suffiecient to explain the observed experimental data [\cite]? Or how collective behavior
 of neurons can be related to stimuli or behavioral tasks [\cite]? These questions 
**********
\mynote{Version 1}
The present note has three nested purposes.
